---
title: "example_cloze"
author: "Dorian"
date: "2024-11-15"
output: html
---

```{r data generation, echo = FALSE, results = "hide"}
mm_o <- 16  # Molar mass of oxygen in g/mol
moles <- 10  # Given moles of water
mass_o <- moles * m_o
```

```{r answers/solutions, echo = FALSE, results = "hide"}
# Initialize lists for the questions, answers, solutions, types, explanations, and tolerances
answers <- list()
solutions <- list()
types <- list()
explanations <- list()
tolerances <- list()

# Define Question 1: Numeric
# Mass of oxygen?
answers[[1]] <- ""  # No predefined answer for numeric questions
solutions[[1]] <- mass_o  # Correct answer: 8 protons
types[[1]] <- "num"
explanations[[1]] <- "The mass of oxygen is calculated by multiplying the number of moles by the molar mass of oxygen. For 10 moles of water, it is 10 * 16 = 160 g."
tolerances[[1]] <- 0  # No tolerance for numeric answer

# Define Question 2: String
# What is the chemical symbol for oxygen?
answers[[2]] <- ""  # No predefined answer for string questions
solutions[[2]] <- "O"  # Correct answer: O
types[[2]] <- "string"
explanations[[2]] <- "The chemical symbol for oxygen is 'O'."
tolerances[[2]] <- 0

# Define Question 3: Single Choice
# To which group does oxygen belong in the periodic table?
answers[[3]] <- c("Noble gases", "Halogens", "Chalcogens", "Alkali metals")
solutions[[3]] <- c(FALSE, FALSE, TRUE, FALSE)  # Correct answer: Chalcogens
types[[3]] <- "schoice"
explanations[[3]] <- solutions[[3]]
tolerances[[3]] <- 0

# Define Question 4: Multiple Choice
# In which of the following compounds is oxygen present?
answers[[4]] <- c("Water", "Carbon dioxide", "Methane", "Sulfur dioxide")
solutions[[4]] <- c(TRUE, TRUE, FALSE, TRUE)  # Correct answers: H2O, CO2, SO2
types[[4]] <- "mchoice"
explanations[[4]] <- c("H2O", "CO2", "SO2", "CH4")
tolerances[[4]] <- 0

```

Question
========

*Questions 1*

Calculate the mass of oxygen in 10 moles of water (H₂O). The molar mass of oxygen is 16 g/mol.
##ANSWER1##

*Question 2*

What is the chemical symbol for oxygen?

##ANSWER2##

*Question 3*

To which group does oxygen belong in the periodic table?

##ANSWER3##

*Question 4*

In which of the following compounds is oxygen present?

##ANSWER4##

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(unlist(answers), markup = "markdown")
```

Solution
========
```{r solutionlist, echo = FALSE, results = "asis"}
# Convert solutions to "True" or "False"
explanations[3] <- lapply(explanations[3], function(x) ifelse(x, "True", "False"))

for (x in 1:length(solutions)) {
  if (types[x] %in% c("schoice", "mchoice")) {
    solutions[x] <- solutions[x] |>
      unlist() |>
      mchoice2string()
  }
}

# Display explanations
answerlist(unlist(explanations), markup = "markdown")
```

Meta-information
================
exname: example_cloze
extitle: oxygen in chemistry 
extype: cloze
exsolution: `r paste(solutions, collapse = "|")`
exclozetype: `r paste(types, collapse = "|")`
extol: `r paste(tolerances, collapse = "|")`
exshuffle: TRUE
exversion: v1